Git Learning Notes

### 2014-01-26 foo.tex
more tutorial note

\end{lstlisting}

@@

\begin{table}
  \caption{Commands}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Command                            & Function \\
    \midrule
    gitk\textsuperscript{\emph{a}}   & Visualization versioning history  \\
    git status\textsuperscript{\emph{b}} & current working flow state \\

>>>>

ssh-keygen -t rsa -C "qisaiman@gmail.com"

% checkout from github 
git add remote hw https://github.com/qisaiman/hw.git
git fetch hw master or develop 
git push hw master
\end{lstlisting}

Git protocol 9148 port.

@@

\begin{table}
  \caption{Commands}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Command                            & Function \\
    \midrule
    gitk\textsuperscript{\emph{a}}   & Visualization versioning history  \\
    git status\textsuperscript{\emph{b}} & current working flow state \\
    ssh key   & zgcss627\\
